Cognitive Analysis

### 2024-10-24 Manuscript Analysis/manuscript_analysis.Rmd
edited a few figures

@@

process_predicted_values |>
  ggplot() +
  aes(x = pattern_c,
      y = fit,
      color = speaker,
      linetype = rep_acc) +
  geom_line(size = .8) +
  theme_bw() +
  theme(aspect.ratio = 1,
        legend.position = "bottom") +
  labs(x = "Processing Speed",
       y = "Pupil Dilation (Arbitrary Units)",
       color = "Speaker",
       linetype = "Repetition Accuracy") +
  scale_color_manual(values = c(my_pal[1], my_pal[2]))

@@

# Merge PLE data with rep acc and listener cog

@@

>>>>

ggsave("Figures/pupil_dilation_plot.png", plot = last_plot())

@@

process_predicted_values |>
  ggplot() +
  aes(x = pattern_c,
      y = fit,
      color = speaker,
      linetype = rep_acc) +
  geom_line(size = .8) +
  theme_bw() +
  theme(aspect.ratio = 1,
        legend.position = "bottom") +
  labs(x = "Processing Speed",
       y = "Pupil Dilation (Arbitrary Units)",
       color = "Speaker",
       linetype = "Repetition Accuracy") +
  scale_color_manual(values = c(my_pal[1], my_pal[2]), labels = c("Neurotypical", "ALS"))

ggsave("Figures/processing_speed_pupil.png", plot = last_plot())

@@

@@

ple |>
  dplyr::group_by(speaker, rep_acc) |>
  dplyr::summarize(per_effort = mean(effort_rating, na.rm = T), 
                   sd = sd(effort_rating, na.rm = T),
                   se = sd/sqrt(n())) |>
  ggplot() +
   aes(x = rep_acc,
       y = per_effort,
       group = speaker,
       color = speaker,
       fill = speaker) +
  geom_bar(stat = "identity", alpha = 0.6, position = position_dodge()) +
  geom_errorbar(aes(ymin = per_effort - se, ymax = per_effort + se), width = 0.4, position = position_dodge(.9)) +
  labs(x = "Accuracy", y = "Perceived Listening Effort Rating", color = "Speaker", fill = "Speaker") +
  theme_bw() +
  theme(aspect.ratio = 1) +
  scale_color_manual(values = c(my_pal[1], my_pal[2]), labels =  c("Neurotypical", "ALS")) +
  scale_fill_manual(values = c(my_pal[1], my_pal[2]), labels = c("Neurotypical", "ALS"))

ggsave("Figures/ple_plot.png", plot = last_plot())
